\begin{vitae}
\addcontentsline{toc}{chapter}{Curriculum Vitae}

\begin{vitaesection}{Education}
\vspace{-0.1cm}
\item [2019] Ph.D. in Physics (Expected), University of California, Santa Barbara.
\item [2017] M.Sc. in Physics, University of California, Santa Barbara.
\item [2014] B.Sc. in Physics, Texas A\&M University, College Station, TX.
\end{vitaesection}

\textbf{Publications}

% \nobibliography*
% \begin{itemize}
%     \item \bibentry{GAN:LHC2019} % http://inspirehep.net/record/1714018
%     \item \bibentry{CMS:myTOPRun2PAS} % http://inspirehep.net/record/1726177
%     \item \bibentry{CMS:mySUSRun2PAS} % http://inspirehep.net/record/1726691
%     \item \bibentry{CMS:myTOP2016} % http://inspirehep.net/record/1633423
%     \item \bibentry{CMS:mySUS2016} % http://inspirehep.net/record/1594731
% \end{itemize}


    \begin{itemize}
        \item B. Hashemi, N. Amin, K. Datta, D. Olivito, and M. Pierini, \textit{LHC analysis-specific datasets with Generative Adversarial Networks} [\href{https://arxiv.org/abs/1901.05282}{arXiv:1901.0528}] \textbf{In progress}
        \item CMS Collaboration, \textit{Search for standard model production of four top quarks in final states with same-sign and multiple leptons in proton-proton collisions at \sthirteen} 
            [\href{http://inspirehep.net/record/1726177}{PAS TOP-18-003}] \textbf{In progress}
        \item CMS Collaboration, \textit{Search for physics beyond the standard model in events with two same-sign leptons or at least three leptons and jets in proton-proton collisions at \sthirteen} 
            [\href{http://inspirehep.net/record/1726691}{PAS SUS-19-008}] \textbf{In progress}
        \item CMS Collaboration, \textit{Search for standard model production of four top quarks with same-sign and multilepton final states in proton-proton collisions at \sthirteen},
            \textit{Eur. Phys. J.} \textbf{C78} (2018) 
            [\href{https://arxiv.org/abs/1710.1061}{arXiv:1710.1061}]
        \item CMS Collaboration, \textit{Search for physics beyond the standard model in events with two leptons of same sign, missing transverse momentum, and jets in proton-proton collisions at \sthirteen}
            \textit{Eur. Phys. J.} \textbf{C77} (2017) 
            [\href{https://arxiv.org/abs/1704.07323}{arXiv:1704.07323}]
    \end{itemize}

\end{vitae}
